TEMPERATURES AND METALLICITIES FOR 10,000+ M DWARFS IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
add test result table

>>>>

\begin{longrotatetable}
\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{Temperatures/Metallicities (from Mann-trained model), and spectral types (from West-trained model) for the sample 10,311 APOGEE M dwarfs. \label{test_results_table}}
\tablehead{\colhead{ID} & \colhead{GAIA ID} & \colhead{RA}  & \colhead{DEC} & \colhead{\teff} 
& \colhead{[FE/H]}  & \colhead{SPT} & \colhead{$\chi^2$ Mann} & \colhead{$\chi^2$ West} }   
\startdata
2M00432365+0332534 & 413814124681430528  & 10.848967  & 3.548273   & 3417 & 0.18  & 2.965025337011196  & 7910  & 7912   & \nodata \\
2M10382316+2457051 & 808931427773946112  & 159.596215 & 24.951373  & 3358 & -0.25 & 3.3883746019230694 & 19051 & 25518  & \nodata \\
2M09364698+5602332 & 598955557617293440  & 144.195513 & 56.042461  & 3819 & 0.01  & 1.502939477318542  & 7981  & 6894   & \nodata \\
2M12165176+1543232 & 1538883006881701120 & 184.215466 & 15.723067  & 3948 & 0.16  & 0.7043011669552124 & 25354 & 19983  & \nodata \\
2M18501195+4809327 & 2037435595069990016 & 282.549868 & 48.15976   & 3899 & 0.24  & 0.9072125957953339 & 7205  & 7151   & \nodata \\
2M07572656+4703318 & 682241540493118080  & 119.360502 & 47.05852   & 3636 & -0.17 & 2.415889813904016  & 38430 & 45625  & \nodata \\
2M11083992+1112503 & 1536026200794333696 & 167.166344 & 11.213979  & 3949 & 0.1   & 0.838691017104972  & 21165 & 17506  & \nodata \\
2M12135300+1419452 & 3695183295027782656 & 183.470871 & 14.32924   & 3824 & 0.13  & 1.3034741941684376 & 35018 & 21010  & \nodata \\
2M12273816-0049437 & 3682549562826659456 & 186.909269 & -0.828949  & 3715 & 0.04  & 1.8358346554321001 & 14179 & 10656  & \nodata \\
2M10513639-0150064 & 777824835073481984  & 162.901465 & -1.835273  & 3997 & -0.15 & 1.1662375752059775 & 80915 & 75157  & \nodata \\
2M02442390-1352593 & 447040266556331008  & 41.099824  & -13.883403 & 3676 & -0.28 & 2.3153986696257274 & 41375 & 56704  & \nodata \\
2M06281785+0940439 & 65792100044278400   & 97.074558  & 9.678234   & 3659 & -0.29 & 2.3027385897344397 & 78827 & 118883 & \nodata \\
2M13441275+5538012 & 1551387099791031552 & 206.053693 & 55.633288  & 3856 & -0.1  & 1.60734737714035   & 50070 & 45895  & \nodata \\
2M12473762+1107449 & 1251277737449848064 & 191.906593 & 11.129187  & 3244 & -0.42 & 3.977729233180596  & 30184 & 47020  & \nodata \\
2M01274162+8435576 & 523638809262601216  & 21.924655  & 84.599233  & 3534 & 0.07  & 2.5591246570653587 & 15529 & 15113  & \nodata \\
2M13464494+4034158 & 1247733770955275008 & 206.686943 & 40.571056  & 3731 & -0.16 & 2.0561869363413123 & 53196 & 50765  & \nodata \\
2M00504161+0219408 & 2376325179183866240 & 12.673481  & 2.327846   & 3745 & 0.4   & 1.4277181066664462 & 76966 & 52035  & \nodata \\
2M14494090+3201268 & 1292097793826595328 & 222.420454 & 32.023994  & 3228 & 0.0   & 3.8941824890924712 & 28733 & 38112  & \nodata \\
2M16434969-0123117 & 1406510018874952960 & 250.957083 & -1.386602  & 3669 & 0.03  & 2.0451626775241616 & 22346 & 17186  & \nodata \\
2M13444356+1655384 & 1565587017583214464 & 206.18144  & 16.927287  & 3652 & 0.13  & 2.0792998403425385 & 47828 & 40933  & \nodata \\
2M08162613+3250515 & 3053990410555781120 & 124.108745 & 32.84736   & 3837 & -0.15 & 1.7923250253907956 & 30389 & 35103  & \nodata \\
2M10414608+2435412 & 3758656623830055168 & 160.441928 & 24.594731  & 4020 & -0.19 & 1.0546884549827298 & 41857 & 36934  & \nodata \\
2M14373854+5014502 & 1188221157913600384 & 219.410555 & 50.247523  & 3380 & -0.13 & 3.224522283084183  & 35397 & 41989  & \nodata \\
2M13444572+0012349 & 1475140469529542656 & 206.19035  & 0.209419   & 3782 & -0.28 & 1.9568926444705497 & 12155 & 12707  & \nodata \\
2M21275902+1332166 & 1817731181599810944 & 321.995889 & 13.537918  & 3997 & 0.18  & 0.6483601588618648 & 78906 & 67503 & \nodata \\
\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
\enddata
\end{deluxetable*}
\end{longrotatetable}
